Discovering Focused Microgenre Communities: Toy example

### 2023-05-17 02_toy-ex.qmd
Updated toy example and link clustering function

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library("fastcluster")
    library("factoextra")
    library("here")
    library("ggplot2")
    library("sjPlot")
    source(here("R", "Functions", "link.dist.R"))
```

# Link Clustering (Toy Example)
```{r Link Clustering toy example}
    x <- c(0, 1, 1, 0, 
           0, 0, 0, 1, 
           1, 1, 1, 1, 
           1, 0, 0, 1, 
           0, 0, 1, 1)
    x <- matrix(x, nrow = 5, ncol = 4,  byrow = TRUE) #toy data
    ldist.res <- link.dist(x = x, id = c(1:5)) #link distance matrix
    hc.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering
```

>>>>

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library("fastcluster")
    library("factoextra")
    library("here")
    library("ggplot2")
    library("sjPlot")
    source(here("Functions", "link.dist.R"))
```

# Link Clustering (Toy Example)
```{r Link Clustering toy example}
    x <- c(0, 1, 1, 0, 
           0, 0, 0, 1, 
           1, 1, 1, 1, 
           1, 0, 0, 1, 
           0, 0, 1, 1)
    x <- matrix(x, nrow = 5, ncol = 4,  byrow = TRUE) #toy data
    ldist.res <- link.dist(x = x, id = c(1:5), null = 1) #link distance matrix
    hc.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering
```
